% !TeX spellcheck = en_GB
% !TEX program = xelatex+makeindex+bibtex
% !TeX TXS-program:pdflatex = txs:///xelatex %
\documentclass[final,a4paper]{report} %scrreprt of scrartcl
\input{../../../library/preamble.tex}
\input{../../../library/style.tex}
\addbibresource{../../../library/bibliography.bib}
\author{Fairphone Repair Group}
\title{Fairphone Repairability}
\date{\today}
\begin{document}
	\section{Becoming a Trusted Distributor}
	\label{sec:becoming-td}
	Simon (section \ref{sec:storyboard-personas}) would like to contribute to Fairphones' good doing by becoming the bridge between the customers and the company. His function will involve two aspects: Providing hardware and service to customers. However, he first needs to be selected to be come a Trusted Distributor (TD) by Fairphone.
	
	Since Simon is to become a valuable member of the Fairphone society, it is very important for him to be reliable and loyal. One of the possible ways to get selected, is by being a helpful member on the Fairphone forums. Being prepared to help people and having a high activity shows commitment and good-will. This would result into being asked by the company to assume the position od TD. An other way could be through application. Just like for a normal job. 
	
	Of course not everyone can become a TD. This function should be special since a TD is provided with a repair kit and will receive a set of all the most up-to-date components and will restocked through the customers order. This system will allow for the phone to be repaired as soon as a couple of hours. 
	
	The TD will follow a crash-course on how to take them apart and put them back together correctly. The amount of TDs per city is defined by the amount of Fairphone owners in that particular city. The more people own a phone, the more TDs are required to meet the supply/demand requirements. The amount of Fairphone owners in a city is determined through the Fairphone mobile registration which takes place when the product is purchased. On the registration, the motivation for the question will be stated, for instance: ``\textit{Fairphone requires this information in order to help you through the Trusted Distributor network}''.
\end{document}