% !TeX spellcheck = en_GB
% !TEX program = xelatex+makeindex+bibtex
% !TeX TXS-program:pdflatex = txs:///xelatex %
\documentclass[final,a4paper]{report} %scrreprt of scrartcl
\input{../../library/preamble.tex}
\input{../../library/style.tex}
\addbibresource{../../library/bibliography.bib}
\author{Fairphone Repair Group}
\title{Fairphone Repairability}
\date{\today}
\begin{document}
	\chapter{FairPoints}
	\label{ch:fairpoints}

	Fairphone, as a start-up company, does not have much financial capability to expand their company in a short period of time. For them, this means that they either slowly increase, or get free contributors to help them due to their nature. In order to help them to spread their words out, the group has come up with a system. In this system, the company will look for people who are willing to help them, with expectancy of getting something in return. This is where FairPoints comes into play. The purpose of FairPoints is rewarding the TD's for their contribution to the ecosystem through virtual credits which they can then spend on the Fairphone forum web-store, or donate to causes Fairphone supports. TD and non-TD will all be able to be a part of this system where different types of contributions to the Fairphone community will be rewarded with a proportional amount of FairPoints. This should be able to keep these contributors more motivated and hence contribute even more in the future. The FairPoints can later be exchanged with the company, for instance on the forum. They could be used to reduce some costs on the next purchase of a certain Fairphone product. Fairphone could also partner up with different charities so that the owner of FairPoints could use this as donation as well. 
	
	The main reason the concept of FairPoints was not taken further into the project was simply due to the fact that it did not fit entirely into the main goal of the project. The main goal at the end is to create a concrete physical product that improves and facilitates the DIY repair experience of their broken/outdated Fairphone. 
\end{document}