%!TEX program = xelatex+makeindex+bibtex
%!TEX spellcheck = en_GB
\documentclass[final,a4paper]{report} %scrreprt of scrartcl
\input{../../library/preamble.tex}
\input{../../library/style.tex}
\addbibresource{../../library/bibliography.bib}
\begin{document}
\chapter{Introduction}\label{ch:introduction} %TODO Vincent
In a world where technology is becoming a bigger part of our lives as the years go by, the mobile phone has risen to be on of the most used items in an average persons life. As a phone company like Fairphone, it is not only very important to make the costumer happy with the their purchase, but also to keep them happy after they have bought it. The best way to do this is with good costumer service. Fairphones' name states its purpose: everything in the company is done under the logo of fair trade, creating an altruistic image for themselves and they are looking for ways to improve themselves in that aspect even further.

Fairphone has given the task to find a way to make the costumer service a pleasant experience for the client. This is very important because in many cases the costumer requires service after a bad experience with the product, for instance, breaking a component. This is the starting point of the journey. Right after the client has broken his phone, it should be possible for him to quickly and painlessly change the broken part in a reasonable amount of time. 

Replacing the broken part currently consists of bringing the phone to the store, and having it sent back to the manufacturer to replace the part. This is usually expensive, as if that isn't enough, it also takes long. With this investigation, methods of improving the efficiency of this process are looked at, in order to turn it into a more pleasant economic experience. However, the phone parts still have to be transported from A to B, therefore, the transportation efficiency will be looked at too, and where possible, improvements are made to decrease the current impact on the environment and making it more efficient for a quicker delivery.

Improving all these aspects should provide the costumer with a more positive experience, and turning the frown from the accident into a smile by economically, quickly and efficiently repairing his phone.
\end{document}