% !TeX spellcheck = en_GB
% !TEX program = xelatex+makeindex+bibtex
% !TeX TXS-program:pdflatex = txs:///xelatex %
\documentclass[final,a4paper]{report} %scrreprt of scrartcl
\input{../../../library/preamble.tex}
\input{../../../library/style.tex}
\addbibresource{../../../library/bibliography.bib}
\author{Fairphone Repair Group}
\title{Fairphone Repairability}
\date{\today}
\begin{document}
	\section{Repairing}
	\label{sec:storyboard-repairing}
The repair is the main focus of the project. For this step in the repairing process two prototypes have been developed (chapters \ref{ch:packaging} and \ref{ch:scrw-it}). These prototypes focus on improving the users experience in the case he performs a DIY. The TD's will have the items as well as they will be included in the phones cost and be a part of the purchase.

In order to meet the 30 minute repairing requirement, special packaging has been developed (chapter \ref{ch:packaging}). This box will contain trays which have slots laid out in the order the phone is taken apart completely. This gives the package an incentive to keep it, and to use it again to speed up the dis/reassembly of the phone.

The second product is a bit more complex (chapter \ref{ch:scrw-it}). It's the size of a credit card so that it can fit in a walled, and holds the screwdrivers required to disassemble the phone, the diagnostics soft/hardware and serves as the Fairphone business card. This product is necessary for the diagnosing of the phone's failure.

The other product that we mention are recommendations on how it could be implemented to make the system complete. There will be no prototypes. 
\end{document} 