%!TEX program = xelatex+makeindex+bibtex
%!TEX spellcheck = en_GB
\documentclass[final]{scrreprt} %scrreprt of scrartcl
\input{../../library/preamble.tex}
\input{../../library/style.tex}
\addbibresource{../../library/bibliography.bib}
\begin{document}
\chapter{Transportation} %TODO Lian Wouter
\label{ch:transportation}

This part was all about finding the most eco-friendly way of transporting the Fairphones.
The most common used ways of shipment would be by aeroplane or by containership.
The location from where the phones were being shipped was the first thing that needed to be clear. 
The Fairphone website states that they have factories in Shenzhen and Chongqing. 
Then the assumption was made that Shenzhen would be the place from where the phones would be shipped to Rotterdam. 
A comparison would have to be made between the eco-impact of shipping by air and overseas.  

To compare these two properly a unit of measurement was needed.
This unit was chosen to be the amount of CO\textsubscript{2} emissions (in grams) per gram of product that needs to be transported.
In order to calculate this properly the following information was needed:

\begin{itemize}
\item Air cargo container volume: \SI{4.32}{\cubic\meter}
\item Air cargo maximum weight: \SI{2450}{\kilo\gram}
\item Fairphone package dimensions: \SI{150}{\milli\meter} x \SI{90}{\milli\meter} x \SI{30}{\milli\meter}
\item Fairphone weight with package: \SI{300}{\gram}
\end{itemize}
Then the assumption was made that the Fairphones would be shipped in batches of \num{8000} units, since there were \num{25000} units produced in total.

Assumed was also that \SI{80}{\percent} of the \num{25000} units would be bought by Dutch and German customers and that the other \SI{20}{\percent} of the customers would be overseas.
The population of Germany and the Netherlands are \num{80.6} and \num{16.8} million persons.
Using this ratio it was calculated that approximately \num{16551} units needed to be shipped to Germany and \num{3448} units to the Netherlands. 

The same location/inhabitant ratio was used the calculate the amount of devices that needed to be shipped to each city, for instance \num{20} units would be needed in Delft.

When the average transport distance from Rotterdam to the city where the customer would be located was calculated the eco-impact could be calculated.
 
The shipping by plane would result in an eco-impact of \SI{4.16}{\gram} of CO\textsubscript{2} per g of product being shipped.
The shipping by containership would result in an eco-impact of \SI{0.44}{\gram} of CO\textsubscript{2} per g of product.

These numbers showed that shipping your products by containership is a lot less harmful to the environment so this was chosen to be the method of transportation.

\end{document}