%!TEX program = xelatex+makeindex+bibtex
%!TEX spellcheck = en_GB
\documentclass[final]{scrreprt} %scrreprt of scrartcl
\input{../../library/preamble.tex}
\input{../../library/style.tex}
\addbibresource{../../library/bibliography.bib}
\begin{document}
\chapter{Diagnostics and Ordering} %TODO Erwin
\label{ch:diagnostics-ordering}

\section{Diagostics}
Diagnosing the problem is a very important part of the process.
This is the first experience the customers has with the system.

The problem with diagnosing is that the phone is very complicated and a lot can go wrong.
It is important to make sure that the customer does not have to deal with the complications.
The way diagnostics are going to be done, is a two part strategy. Prevention is better than cure.

\subsection{Part One: Prevention}
The phone itself can constantly watch it's hardware and warn the user as soon as something might go wrong in the near feature, both in software and in hardware.
Because Fairphone has full control over the software in the Fairphones, they can install the necessary software to accomplish this.
The prevention system can use telemetry data gathering techniques to detect the health of the hardware.

\subsection{Part Two: Cure}
When something does unexpectedly go wrong and the phone still has it's basic functions.
Then the software can present the user with the information the user need to remedy the problem.
In the event that the hardware is no longer able to self-diagnose.
We need an external device to run the diagnosis.
This can be in the form of a computer or an other phone.
This will plug seamlessly into the ordering system to give the user that best experience possible.
After that the ordering system will handle everything up to delivery.

\section{Ordering} %TODO Erwin
The ordering system will get the information about the diagnosed problem.
It will present the user with all the necessary information to complete the order and delivery.
If the user is near a Trusted Distributor (see Chapter \ref{ch:trusted-distributors})

\end{document}